Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-07 thesis/paper.tex
Methodology re-write

\smallskip \noindent
\textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results of the study around already established and accepted software evolution theories \cite{chapin2001types} \cite{lehman1980programs}. Due to restricted access to the company's source code, we were not able to include versions previous to version 1.4 in our analysis. This means that the evolution of the API was studied during a rather short part of its lifetime ( "rephrase"). It was also not possible to analyse the implementation of the API, something which might have contributed to more accurate predictions of the motives behind the changes. We consider this to be remaining threats to construct validity.

\smallskip \noindent
\textbf{Internal validity  } Internal validity has been acknowledged by analysing the code and documentation jointly. This has contributed to triangulating the results and discovering possible inconsistencies. Further triangulation of the results was performed by interviewing the API architect. Business-related factors might have had an impact on the evolution of the API, and these were not closely investigated. This was not in the scope of the study and would best be investigated in a study complementary to ours. The study revealed that the API users were significant to the evolution of the API. Since API users were not interviewed, it might be an affecting factor which was left unexplored.

\smallskip \noindent
\textbf{External validity  } The results of our study should be highly generalisable to similar studies conducted on any type of APIs, since the evolution of the API has largely been driven by software-related factors. Our study should be of special interest to researchers studying platform or embedded APIs. The fact that the results of the study are presented in a structured way, by relating them to existing software evolution theories, should further increase the generalisability of our study.

>>>>

\noindent
\textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results the study around already established and accepted theories \cite{chapin2001types} \cite{lehman1980programs}. Due to restricted access to the company's source code, we were not able to include versions previous to version 1.4 in our analysis. This means that the evolution of the API was studied during a rather short part of its lifetime ( "rephrase"). It was also not possible to analyse the implementation of the API, something which might have contributed to more accurate predictions of the motives behind the changes. We consider this to be remaining threats to construct validity.

\smallskip \noindent
\textbf{Internal validity  } Internal validity has been acknowledged by analysing the the code and documentation jointly. This has contributed to triangulating the results and discovering possible inconsistencies. Further triangulation of the results was performed by interviewing the API architect. Business-related factors might have had an impact on the evolution of the API, and these were not closely investigated. This was not in the scope of the study and would best be investigated in a study complementary to ours. The study revealed that the API users were significant to the evolution of the API. Since API users were not interviewed, it might be a affecting factor which was left unexplored.

\smallskip \noindent
\textbf{External validity  } The results of our study should be highly generalisable similar studies conducted on any type of APIs, since the evolution of the API has largely been driven by software-related factors. Our study should be of special interest to researchers studying platform or embedded APIs. The fact that the results of the study are presented in a structured way, by relating them to existing software evolution theories, should further increase the generalisability of our study.
